---
title: "BBets Project"
author: "Brandon Medina"
date: "1/31/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Introduction

The question is how much money is won/lost on a bet that at least two people have the same birthday in a class of 35. Instructor wagers 2:1

Instructor has done this 15 times  
1. What is his expected win/loss amount?  
2. How much would the instructor have to wager to make the bet fair?  
3. How many students would have to be in the class for a 2:1 bet to be fair?  


```{r}
days = 1:365

students = 35
classes = 15
runs = students*classes
payout = 2

SaveArray= vector('numeric')
for(k in 1:1000){
    bank =0
    for(i in 1:runs){
      sampleClass = sample(days, students, replace=TRUE)

      repeats = length(unique(sampleClass))
      if (repeats == students) bank = bank -payout
      else bank = bank +1
  }
SaveArray[k]=bank
}
```

Histogram of bank amounts
```{r}
hist(SaveArray)
```

Answer Question #1

```{r}
print('average amount:')
print(mean(SaveArray))
```

2. 

```{r}
days = 1:365

students = 35
classes = 15
runs = students*classes
payout = 4.39

SaveArray= vector('numeric')
for(k in 1:1000){
    bank =0
    for(i in 1:runs){
      sampleClass = sample(days, students, replace=TRUE)

      repeats = length(unique(sampleClass))
      if (repeats == students) bank = bank -payout
      else bank = bank +1
  }
SaveArray[k]=bank
}
```

Histogram of bank amounts
```{r}
hist(SaveArray)
```

Answer Question #2

```{r}
print('Instructor Wager')
print(payout)

print('average amount:')
print(mean(SaveArray))
```

3.

```{r}
days = 1:365

students = 28
classes = 15
runs = students*classes
payout = 2

SaveArray= vector('numeric')
for(k in 1:1000){
    bank =0
    for(i in 1:runs){
      sampleClass = sample(days, students, replace=TRUE)

      repeats = length(unique(sampleClass))
      if (repeats == students) bank = bank -payout
      else bank = bank +1
  }
SaveArray[k]=bank
}
```

Histogram of bank amounts
```{r}
hist(SaveArray)
```

Answer question #3

```{r}
print('Student Count:')
print(students)
print('average amount:')
print(mean(SaveArray))
```

